---
title: "CLT"
author: "Rabi Elkhoury"
output: html_document
date: 'Suummer 2022'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")

options(digits=1)
```



Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The data is bimodal, indicating that it has two peaks.  The peaks are nearly identical, peaking at densities of about 0.015.  The sample mean is `r mean(my1000)` and the standard deviation is `r sd(my1000)`



Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size?   

This data is trimodal, but more of the data seems to tend more towards being Normal, highlighting the Central Limit Theorem.  The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`




 

Do this again for 4 random samples

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
```
The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`  

Then again for 9 random samples  

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`  


then 16 random samples  

```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`


finally for 36 random samples.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
```

The sample mean is `r mean(x.avg)` and the standard deviation is `r sd(x.avg)`




Write a summary paragraph describing what you observed and how it relates to the central limit theorem.








Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.









